A Context Menu for the Real World: Controlling Physical Devices Through Head-Worn Infrared Targeting

### 2013-09-18 doc/sigchi14/interaction.tex

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/stepbystep.png}
\caption{(A) Glass periodically sends out infrared signal aligned with the direction user is facing. (B) Device toggles red led as visual feedback when receiving valid signals. (C) User taps to connect with responding client}
\label{fig:interaction}
\end{figure}

>>>>

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/stepbystep.png}
\caption{Targeting interaction: when users turn towards a controllable appliance (A->B), the appliance shows immediate visual feedback (B). Users confirm that they wish to connect to this appliance with a tap (C) which triggers connection feedback on the appliance.}
\label{fig:interaction}
\end{figure}
